---
title: "Научный опыт"
author: "Волков Н.П."
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)

style_mono_light()
# usethis::create_project("/Users/nikitavolkov")
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "animate_css", "tachyons"))
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```

```{r xaringan-editable, echo=FALSE}
xaringanExtra::use_editable(expires = 1)
```

```{r broadcast, echo=FALSE}
xaringanExtra::use_broadcast()
```


# Зарубежные публикации

Efficacy and safety of nivolumab combined with brentuximab vedotin after nivolumab monotherapy failure in patients with relapsed and refractory classic Hodgkin lymphoma. International Journal of Clinical Oncology
2021

Immunosuppressive Microenvironment and Efficacy of PD-1 Inhibitors in Relapsed/Refractory Classic Hodgkin Lymphoma: Checkpoint Molecules Landscape and Macrophage Populations. Cancers
2021

Nivolumab in Primary CNS Lymphoma and Primary Testicular Lymphoma with CNS Involvement: Single Center Experience. Blood
2020

Safety of Allogeneic Stem Cell Transplantation after PD-1 Blockade for Patients with Relapsed/Refractory Classical Hodgkin Lymphoma: Focus on Immune-Related Adverse Events. Blood
2020

A Phase 2 Study of Nivolumab Using a Fixed Dose of 40mg (Nivo40) in Patients With Relapsed/Refractory Hodgkin Lymphoma. HemaSphere
2020


---

# Фармакоэкономика 

First-Line Treatment of Mantle-Cell Lymphoma: Analysis of Effectiveness and Cost-Effectiveness. Clinical Oncohematology
2018 

Hodgkin’s Lymphoma: Analysis Results of Volgograd Regional Registry. Clinical oncohematology
2019

Analysis Results of the Regional Registry of Patients with Diffuse Large B-cell Lymphoma: Risk Factors and Chemo-Immunotherapy Issues. Clinical oncohematology
2019 

---

# Популяционные и другие исследования

Achievements and Challenges of Evidence-Based Medicine in Hematopoietic Stem Cell Transplantation: An Analysis of Single-Center and Multicenter Trials. Clinical oncohematology
2020 

Clinical efficiency and safety of tramadol and low-dose morphine to manage pain syndromes in children following chemotherapy and hematopoietic stem cell transplantation. Cellular Therapy and Transplantation
2020

Long-Term Outcomes of Nivolumab Therapy in Patients with Relapsed/Refractory Classic Hodgkin’s Lymphoma after High-Dose Chemotherapy with Autologous Hematopoietic Stem Cell Transplantation in Real Clinical Practice. Clinical oncohematology
2020 

Prognostic factors and effectiveness of the first-line therapy for chronic lymphocytic leukemia: results of 10-year follow-up. The Scientific Notes of the Pavlov University
2021

---

